---
title: "Data about cars"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE, message = F, warning = F}
# This is a comment, because it comes after a # symbol. 
# The computer ignores comments, even though they are within code chunks. 

# Set working directory, if needed
# setwd(...)

# Install packages if needed
if (!require(flexdashboard)) install.packages('flexdashboard')
if (!require(knitr)) install.packages('knitr')
if (!require(DT)) install.packages('DT')
if (!require(dplyr)) install.packages('dplyr')
if (!require(scales)) install.packages('scales')
if (!require(plotly)) install.packages('plotly')
if (!require(plyr)) install.packages('plyr')
if (!require(treemap)) install.packages('treemap')
if (!require(highcharter)) install.packages('highcharter')
if (!require(factoextra)) install.packages('factoextra')

# Load packages
library(flexdashboard)
library(knitr)
library(DT)
library(dplyr)
library(scales)
library(plotly)
library(plyr)
library(treemap)
library(highcharter)

# Load data (put code to load from Excel or CSV here, if needed)
d <- mtcars

# Do any required pre-processing
d.scaled <- as.data.frame(scale(mtcars))
```


# Dashboard Information

## Column 1 {data-width=500}

### Data information

Description of the data, from the authors: The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

These are the variables in the data:

*	mpg	Miles/(US) gallon
*	cyl	Number of cylinders
*	disp	Displacement (cu.in.)
*	hp	Gross horsepower
*	drat	Rear axle ratio
*	wt	Weight (1000 lbs)
*	qsec	1/4 mile time
*	vs	Engine (0 = V-shaped, 1 = straight)
* am Transmission (0 = automatic, 1 = manual)
*	gear	Number of forward gears
*	carb	Number of carburetors

## Column 2 {data-width=500}

### About the author {data-width=500}

Anshul Kumar

### About the organization

MGH Institute of Health Professions is a graduate school founded by MGH. 

# Explore Data {data-orientation=rows}

## Row 1

### Explore the dataset

```{r}
DT::datatable(d)
```


## Row 2

### Relationship of MPG and weight

```{r}
with(d, plot(mpg~wt))
```


### Distribution by gears and transmission

```{r}
with(d, table(gear,am))
```


# Visualizations

## Column 1  {data.width=500 .tabset .tabset-fade}

### K-means clustering (k=2)

Identify two groups in the data:

```{r}
library(factoextra)
km <- kmeans(d.scaled, centers = 2)
fviz_cluster(km, data = d.scaled)

```

### Transmission by region pie chart

Where each car comes from, divided by transmission type:

```{r}
d$region <- c("Asia","Asia","Asia","North America","North America","North America","North America","Europe","Europe","Europe","Europe","Europe","Europe","Europe","North America","North America","North America","Europe","Asia","Asia","Asia","North America","North America","North America","North America","Europe","Europe","Europe","North America","Europe","Europe","Europe")

d$transmission <- NA
d$transmission[d$am==1] <- "Manual"
d$transmission[d$am==0] = "Automatic"

# with(d, table(am,transmission,useNA = "ifany"))

d$Count <- 1

dout <- data_to_hierarchical(d, c(region, transmission), Count)

hchart(dout, type = "sunburst") %>% hc_legend()

# d$region <- NULL
# d$Count <- NULL
```


## Column 2 {data.width=500}

### Data with clusters

```{r}
d.scaled <- as.data.frame(km$cluster)
d$cluster <- d.scaled$`km$cluster`
d.partial <- subset(d, select=c(mpg,wt,cluster))
DT::datatable(d.partial)
```

